A Topography of Climate Change Research

### 2017-11-14 pres/APSIS_17_11_09.tex
updated pres

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=0.85\linewidth]{../plots/network_wg_372.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item A network of comprehensible topics is generated with 100 topics
				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=0.85\linewidth]{../plots/shares_10_372.PNG}

			\includegraphics[width=0.85\linewidth]{../plots/sustainability.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item In later assessment periods, the largest topic is on research priorities and sustainability
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/top_20_372.png}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item Negative emissions related topics have shown strong growth since the end of AR5
				\item As have topics on cities and extreme weather events
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_topics_65.png}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item ``Niche'' topics on specific technological solutions, are less well covered
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{frame}{Next steps}

\begin{columns}
%	\begin{column}{0.6\linewidth}
%		\begin{center}
%			\includegraphics[width=\linewidth]{../plots/ipcc_topics_65.png}
%		\end{center}
%	\end{column}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\begin{itemize}
				\item Can I get a clearer research question, and make the analysis less descriptive?
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

>>>>

\begin{figure}

	\[V_{i\mu} \]

	\includegraphics[width=\linewidth]{../plots/VWH_blank.png}

	\caption{A topic model of 3495 documents on climate change from the year 2000}

\end{figure}

\begin{figure}

	\[V_{i\mu} \approx (WH)_{i\mu} = \sum_{a=1}^{r}W_{ia}H_{a\mu} \]

	\includegraphics[width=\linewidth]{../plots/VWH.png}

	\caption{A topic model of 3495 documents on climate change from the year 2000}

\end{figure}

\begin{frame}{Research Questions}
\begin{itemize}
	\item What topics are discovered endogenously from a corpus of > 200,000 abstracts on climate change?
	\item How do these topics describe the structure of the literature?
	\item Which topics have grown recently?
	\item Which topics are better and less well represented in IPCC assessment reports?
\end{itemize}

@@

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}	
			\vspace*{-0.1\linewidth}
			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
		\begin{center}
			\begin{itemize}
				\item A network of comprehensible topics is generated with 100 topics
				\item Topics can be matched to the IPCC working group from which the majority of the topic documents are referenced in
				\item Topics from the same working group are \textbf{significantly} more likely to be correlated with each other than those which are not
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - structure - WGI}

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}
			\vspace*{-0.1\linewidth}
			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_1.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
		\begin{center}
			\begin{itemize}
				\item The largest topic in WGI is on models.
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - structure - WGII}

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}
			\vspace*{-0.1\linewidth}
			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_2.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
		\begin{center}
			\begin{itemize}
				\item The largest primarily WGII topic is on climate change impacts
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - structure - WGIII}

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}
			\vspace*{-0.1\linewidth}
			\includegraphics[width=1.1\linewidth]{../plots/network_wg_372_3.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
		\begin{center}
			\begin{itemize}
				\item The largest WGIII topic is on emissions reductions.
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - structure - other clusters}

\begin{columns}
	\begin{column}{0.65\linewidth}
		\begin{center}
			\vspace*{-0.1\linewidth}
			\hspace*{-0.1\linewidth}
			\includegraphics[width=1.25\linewidth]{../plots/network_wg_372_4.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.35\linewidth}
		\includegraphics[width=0.4\linewidth]{../plots/network_wg_key.PNG}
		\begin{center}
			\begin{itemize}
				\item A fourth cluster of mostly WGII references contains topics on ecosystems, species and habitats
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}			
			\includegraphics[width=\linewidth]{../plots/sustainability.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item In later assessment periods, a large meta-topic on research priorities and sustainability emerges
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

@@

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/top_20_386.png}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item Negative emissions related topics have shown strong growth since the end of AR5
				\item As have topics on cities and extreme weather events
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Preliminary results - growth - biochar}

		\begin{center}
			\includegraphics[width=\linewidth]{../plots/biochar_growth.png}

			\begin{itemize}
				\item Biochar has emerged as an entirely new topic in the last 10 years
			\end{itemize}
		\end{center}

@@

How can we get a sense of which topics are better covered in IPCC reports?

\begin{itemize}
	\item Each document \(d\) either matches or does not match an IPCC reference
	\item For each topic \(h\), we can sum the scores for each category of document
	\item The ``IPCC proportion'' of each topic is the proportion of the sum of the document score accounted for by documents which match IPCC references.
\end{itemize}

@@

\begin{columns}
	\begin{column}{0.7\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/ipcc_topics_386.png}
		\end{center}
	\end{column}
	\begin{column}{0.3\linewidth}
		\begin{center}
			\begin{itemize}
				\item The physical science aspects of climate change, as well topics on impacts, adaptation and scenarios are well covered by the IPCC
				\item Topics on specific technological solutions (particularly NETs), as well as soils, are less well covered
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Conclusions}

\begin{itemize}
	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
	\item Topics from the same IPCC working group are more likely to be connected to each other.
	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
\end{itemize}

\begin{frame}{Extra results - Journals}

\begin{columns}
	\begin{column}{0.55\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/journals/journal_papers.png}
		\end{center}
	\end{column}
	\begin{column}{0.45\linewidth}
		\begin{center}
			\begin{itemize}
				\item Nature has been publishing about climate change for a long time
				\item Plos One has very recently overtaken all other journals
				\item The number of journals has risen very steeply
			\end{itemize}
		\includegraphics[width=0.9\linewidth]{../plots/journals/n_journals.png}
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Extra results - Journals}

\begin{columns}
	\begin{column}{0.55\linewidth}
		\begin{center}
			\includegraphics[width=\linewidth]{../plots/journals/journal_entropy_386.png}
		\end{center}
	\end{column}
	\begin{column}{0.45\linewidth}
		\begin{center}
			\begin{itemize}
				\item Journal Entropy describes the distribution of topics in a journal \citep{Hall2008a}
				\item High values mean the journal deals with a wider range of topics
			\end{itemize}
			\[  H(z\rvert c,y) = -\sum_{i=1}^{K} \hat{p}(z_i \rvert c,y) \; log \; \hat{p}(z_i \rvert c, y) \]
		\end{center}
	\end{column}
\end{columns}

\begin{frame}{Extra results - Journals}

	\includegraphics[width=\linewidth]{../plots/journals/journal_topics_386.png}
